\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

Fusing the last 3 steps led to a substantial reduction in the time taken, especially for beam size of 1 where the softmax does not actually have to calculated, Table~\ref{tab:fused-breakdown-europarl} and ~\ref{tab:fused-breakdown-opensubtitles}. This led to an overall increase in translation speed of up to 23\% for the Europarl test set, Figure~\ref{fig:beam-europarl}, and up to 41\% for the OpenSubtitles test set, Figure~\ref{fig:beam-opensubtitles}.

>>>>

Fusing the last 3 steps led to a substantial reduction in the time taken, especially for beam size of 1 where the softmax probability does not actually have to calculated, Table~\ref{tab:fused-breakdown-europarl} and ~\ref{tab:fused-breakdown-opensubtitles}. This led to an overall increase in translation speed of up to 23\% for the Europarl test set, Figure~\ref{fig:beam-europarl}, and up to 41\% for the OpenSubtitles test set, Figure~\ref{fig:beam-opensubtitles}.
